---
title: "Event Study: Parameters"
author: "Dr. Simon Müller"
date: "`r Sys.Date()`"
output:
  rmdformats::html_clean:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    css: kable.css
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Motivation

You can manually adjust all parameters in your R environment. Save this object 
and use it in all your Event Studies. This vignette gives you an overview on how
to set the correct parameters in R.


# Options

You are able to set some general options in the R option object. This enables you
to setup your API credentials for all R sessions. 

- *EventStudy.URL*: The API url (default: http://api.eventstudytools.com)
- *EventStudy.KEY*: The API key (default: NULL)
- *EventStudy.verbose*: Verbose level (range: 1 - 3, default: 3)
- *EventStudy.tryAttempts*: Attempts to retry http request (default: 3)

The options can be changed by the `options` function in R, e.g.

```{r, eval=FALSE}
options(EventStudy.URL = "http://api.eventstudytools.com")
```

The options can be retained by the 

```{r, eval=FALSE}
getOption("EventStudy.tryAttempts")
```


# Performing an Event Study (ARC, AVC, or AVyC)

After you have set your paramaeters, you can easily perform your Event Study:

```{r, eval=FALSE}
apiUrl <- "http://api.eventstudytools.com"
apiKey <- "Please insert your key here"

# Setup API Connection
estSetup <- EventStudyAPI$new()
estSetup$authentication(apiKey)

estSetup$performEventStudy(estParams = volatilityEstParams, 
                           dataFiles = c("request_file" = "01_RequestFile.csv",
                                         "firm_data"    = "02_firmData.csv",
                                         "market_data"  = "03_marketData.csv"))
```


# General Event Study Parameters

There are several parameters that are valid for all type of Event Studies 
(Return, Volatility, and Volume Event Study). Each type of Event Study has its 
own `R6` object that has to be initialized before you want to perform an Event
Study. 

- `ARCApplicationInput`: Return Event Study
- `AVCApplicationInput`: Volume Event Study
- `AVyCApplicationInput`: Volatility Event Study

For the rest of this paragraph, we are working with a Return Event Study object.
All parameters in this section can also applied to the other two objects.

```{r, eval=FALSE}
returnEstParams <- ARCApplicationInput$new()
```

## Return File Type

The return type defines the type of the result file. Possible options are

- **csv** (default): comma-separated file with `;` as delimiter 
- **xls**: Excel 2007 
- **xlsx**: Excel 2010 and newer
- **ods**: OpenOffice Spreadsheet

Usage:
```{r, eval=FALSE}
returnEstParams$setResultFileType("xlsx")
```


## Return Type

- **log** (default): Return calculation by using log
- **simple**: Simple return calculation

Usage:
```{r, eval=FALSE}
returnEstParams$setReturnType("simple")
```


## Adjustment of Non-trading Days

- **earlier**: Take earlier trading day (Pick an earlier date if the event day falls on a non-trading day (e.g., a weekend day))
- **later** (default): Take later trading day (Pick the next trading day if the event day falls on a non-trading day (e.g., a weekend day)).
- **keep**: Keep non-trading day (Keep announcement dates even if they fall on a non-trading day (e.g., a weekend day))
- **skip**: Skip respective observations (Skip observations with event dates falling on non-trading days (e.g., weekends))

Usage:
```{r, eval=FALSE}
returnEstParams$setNonTradingDays("earlier")
```


# Abnormal Return Event Study

For performing Return Event Studies you need to initialize an `ARCApplicationInput`
 R6 object.

```{r, eval=FALSE}
returnEstParams <- ARCApplicationInput$new()
```

## Benchmark Models

- **mm** (default): Market Model
- **mm-sw**: Scholes/Williams Model
- **cpmam**: Comparison Period Mean Adjusted
- **ff3fm**: Fama-French 3 Factor Model
- **ffm4fm**: Fama-French-Momentum 4 Factor Model
- **garch**: GARCH (1, 1) Model
- **egarch**: EGARCH (1, 1) Model

Usage:
```{r, eval=FALSE}
returnEstParams$setBenchmarkModel("mm-sw")
```


## Test Statistics

Per default all test statistics are activated. A detailed description can be 
found on our [website](https://www.eventstudytools.com/significance-tests).

*Parametric Test Statistics:*

- t-Test:
    - art
    - cart
    - abhart
- Cross-Sectional Test (CSect T):
    - aart
    - caart
    - abhart
- Time-Series Standard Deviation or Crude Dependence Test (CDA T):
    - aarcdat
    - caarcdat
- Patell or Standardized Residual Test (Patell Z):
    - aarptlz
    - caarptlz
- Kolari and Pynnönen adjusted Patell or Standardized Residual Test (Adjusted Patell Z):
    - aaraptlz
    - caaraptlz
- Standardized Cross-Sectional or BMP Test (StdCSect Z):
    - aarbmpz
    - caarbmpz
- Kolari and Pynnönen Adjusted Standardized Cross-Sectional or BMP Test (Adjusted StdCSect Z) 
    - aarabmpz
    - caarabmpz
- Skewness Corrected Test (Skewness Corrected T):
    - aarskewadjt
    - caarskewadjt
    - abharskewadjt
- Jackknife Test (Abbr.: Jackknife T) 
    - aarjackknivet
    - caarjackknivet

**Non-Parametric Test Statistics:**

- Corrado Rank Test (Rank Z):
    - aarrankz
    - caarrankz
- Generalized Rank T Test (Generalized Rank T):
    - aargrankt
    - caargrankt
- Generalized Rank Z Test (Generalized Rank Z):
    - aargrankz
    - caargrankz
-  Cowan Generalized Sign Test (Generalized Sign Z) 
    - aargsignz
    - caargsignz

Usage:
```{r, eval=FALSE}
returnEstParams$setTestStatistics(c("aarptlz", "aarrankz"))
```


# Abnormal Volume Event Study

For performing Return Event Studies you need to initialize an `AVCApplicationInput`
 R6 object.

```{r, eval=FALSE}
volumeEstParams <- AVCApplicationInput$new()
```

## Benchmark Models

- **mm** (default): Market Model
- **mm-sw**: Scholes/Williams Model
- **cpmam**: Comparison Period Mean Adjusted
- **ff3fm**: Fama-French 3 Factor Model
- **ffm4fm**: Fama-French-Momentum 4 Factor Model

Usage:
```{r, eval=FALSE}
volumeEstParams$setBenchmarkModel("mm-sw")
```


## Test Statistics

Per default all test statistics are activated. A detailed description can be 
found on our [website](https://www.eventstudytools.com/significance-tests).

*Parametric Test Statistics:*

- t-Test:
    - art
    - cart
    - abhart
- Cross-Sectional Test (CSect T):
    - aart
    - caart
    - abhart
- Time-Series Standard Deviation or Crude Dependence Test (CDA T):
    - aarcdat
    - caarcdat
- Patell or Standardized Residual Test (Patell Z):
    - aarptlz
    - caarptlz
- Kolari and Pynnönen adjusted Patell or Standardized Residual Test (Adjusted Patell Z):
    - aaraptlz
    - caaraptlz
- Standardized Cross-Sectional or BMP Test (StdCSect Z):
    - aarbmpz
    - caarbmpz
- Kolari and Pynnönen Adjusted Standardized Cross-Sectional or BMP Test (Adjusted StdCSect Z) 
    - aarabmpz
    - caarabmpz
- Skewness Corrected Test (Skewness Corrected T):
    - aarskewadjt
    - caarskewadjt
    - abharskewadjt
- Jackknife Test (Abbr.: Jackknife T) 
    - aarjackknivet
    - caarjackknivet

**Non-Parametric Test Statistics:**

- Corrado Rank Test (Rank Z):
    - aarrankz
    - caarrankz
- Generalized Rank T Test (Generalized Rank T):
    - aargrankt
    - caargrankt
- Generalized Rank Z Test (Generalized Rank Z):
    - aargrankz
    - caargrankz
-  Cowan Generalized Sign Test (Generalized Sign Z) 
    - aargsignz
    - caargsignz

Usage:
```{r, eval=FALSE}
volumeEstParams$setTestStatistics(c("aarptlz", "aarrankz"))
```


# Abnormal Volatility Event Study

For performing Return Event Studies you need to initialize an `AVyCApplicationInput`
 R6 object.

```{r, eval=FALSE}
volatilityEstParams <- AVyCApplicationInput$new()
```

## Benchmark Models

- **garch** (default): Garch(1, 1) Model


## Test Statistics

Per default all test statistics are activated. A detailed description can be 
found on our [website](https://www.eventstudytools.com/volatiliy-event-study).

**Volatility Test Statistics:**

- Cross-Sectional Test for Abnormal Volatility
    - aarcsvyt
- Corrected Cross-Sectional Test for Abnormal Volatility
    - aarcscvyt
- AAR Volatility Ratio-Test
    - aarlambdaz

**Abnormal Return Test Statistics:**

- Cross-Sectional Test for Abnormal Return
    - aarcsart
- Cross-Sectional-Corrected Test for Abnormal Return
    - aarcscart

Usage:
```{r, eval=FALSE}
volatilityEstParams$setTestStatistics(c("aarptlz", "aarrankz"))
```
