---
title: "Event Study: Parameter"
author: "Dr. Simon Müller"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: kate
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Motivation

You can manually adjust all parameters in your R environment. Save this object 
and use it in all your Event Studies. This vignette gives you an overview on how
to set the correct parameters in R.


# General Parameters

There are several parameters that are valid for all type of Event Studies 
(Return, Volatility, and Volume Event Study). Each type of Event Study has its 
own `R6` object that has to be initialized before you want to perform an Event
Study. 

- `ESTARCParameters`: Return Event Study
- `ESTAVyCParameters`: Volatility Event Study
- `ESTAVParameters`: Volume Event Study

For the rest of this paragraph, we are working with a Return Event Study object.
All parameters in this section can also applied to the other two objects.

```{r, eval=FALSE}
retEstParam <- ESTARCParameters$new()
```

## Return File Type

The return type defines the type of the result file. Possible options are

- **csv** (default): comma-separated file with `;` as delimiter 
- **xls**: Excel 2007 
- **xlsx**: Excel 2010 and newer
- **ods**: OpenOffice Spreadsheet

Usage:
```{r, eval=FALSE}
retEstParam$setResultFileType("xlsx")
```

## Handling Non-trading Days

- **earlier**: Take earlier trading day
- **later** (default): Take later trading day
- **keep**: Keep non-trading day
- **skip**: Skip respective observations

Usage:
```{r, eval=FALSE}
retEstParam$setNonTradingDays("earlier")
```


## Return Type

- **log** (default): Return calculation by using log
- **simple**: Simple return calculation

Usage:
```{r, eval=FALSE}
retEstParam$setReturnType("simple")
```

## Task

In the task parameter list you can define the locale (currently just `en` is possible)
and the email address (currently not working). If an email address is defined, 
you get an email when the calculation is finished.


# Return Event Study

For performing Return Event Studies you need to initialize an `ESTARCParameters`
 R6 object.

```{r, eval=FALSE}
retEstParam <- ESTARCParameters$new()
```

## Benchmark Models

- **mm** (default): Market Model
- **mm-sw**: Scholes/Williams Model
- **cpmam**: Comparison Period Mean Adjusted
- **ff3fm**: Fama-French 3 Factor Model
- **ffm4fm**: Fama-French-Momentum 4 Factor Model
- **garch**: GARCH (1, 1) Model
- **egarch**: EGARCH (1, 1) Model

Usage:
```{r, eval=FALSE}
retEstParam$setBenchmarkModel("mm-sw")
```


## Test Statistics

Per default all test statistics are activated. A detailed description can be 
found on our [website](https://www.eventstudytools.com/significance-tests).

*Parametric Test Statistics:*

- t-Test:
    - art
    - cart
    - abhart
- Cross-Sectional Test (CSect T):
    - aart
    - caart
    - abhart
- Time-Series Standard Deviation or Crude Dependence Test (CDA T):
    - aarcdat
    - caarcdat
- Patell or Standardized Residual Test (Patell Z):
    - aarptlz
    - caarptlz
- Kolari and Pynnönen adjusted Patell or Standardized Residual Test (Adjusted Patell Z):
    - aaraptlz
    - caaraptlz
- Standardized Cross-Sectional or BMP Test (StdCSect Z):
    - aarbmpz
    - caarbmpz
- Kolari and Pynnönen Adjusted Standardized Cross-Sectional or BMP Test (Adjusted StdCSect Z) 
    - aarabmpz
    - caarabmpz
- Skewness Corrected Test (Skewness Corrected T):
    - aarskewadjt
    - caarskewadjt
    - abharskewadjt
- Jackknife Test (Abbr.: Jackknife T) 
    - aarjackknivet
    - caarjackknivet

**Non-Parametric Test Statistics:**

- Corrado Rank Test (Rank Z):
    - aarrankz
    - caarrankz
- Generalized Rank T Test (Generalized Rank T):
    - aargrankt
    - caargrankt
- Generalized Rank Z Test (Generalized Rank Z):
    - aargrankz
    - caargrankz
-  Cowan Generalized Sign Test (Generalized Sign Z) 
    - aargsignz
    - caargsignz

Usage:
```{r, eval=FALSE}
retEstParam$setTestStatistics(c("aarptlz", "aarrankz"))
```
